Ms 1

### 2017-11-01 ms1/ms1_display.Rmd
collapse

```{r tier_graph}
pde_tier_table = read_tsv('tables/pde_approp_table.tsv') %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

@@

```{r hcpcs_count}
hcpcs_count = read_tsv('tables/hcpcs_count.tsv') %>%
  group_by(hcpcs_flag) %>%
  summarize(n_dx=sum(n_dx)) %>%
  mutate(f=n_dx/sum(n_dx))

@@

This equals a total of `r prettyNum(sum(hcpcs_count$n_dx), big.mark=',')` diagnoses.

>>>>

```{r tier_graph}
pde_tier_table = dx_pde_counts %>%
  filter(has_dx_em) %>%

pde_tier_table = read_tsv('raw_data/dx_pde_counts.tsv') %>%
  group_by(year,

pde_tier_table = read_tsv('tables/pde_approp_table.tsv') %>%
  group_by(year, antibiotic) %>%
  mutate(f=n/sum(n)) %>%
  ungroup()

@@

```{r hcpcs_count}
encounter_counts = read_tsv('raw_data/dx_cat_count.tsv') %>%
  summarize(n_encounters=sum(n_encounters),
            n_em_encounters=sum(n_encounters[hcpcs_em]),
            f_em_encounters=weighted.mean(hcpcs_em, weights=n_encounters))

@@

This equals a total of `r prettyNum(sum(encounter_counts$n_encounters), big.mark=',')` encounters.
